---
title: "First-year distribution and movement rates of PIT-tagged North East Atlantic mackerel (Scomber Scombrus) varies with timing, location, and fish size at release during the spawning season"

output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



*Contributors: Kotaro Ono<sup>1†</sup>, Sondre Hølleland<sup>1†</sup>, Aril Slotte<sup>1</sup>,....* 

  *<sup>1</sup>Institute of Marine Research.* 
  
  *<sup>†</sup> Responsible for the code.* 

  *Correspondance to: kotaro.uno@hi.no*
 
 *Paper can be found [here](https://www.hi.no) (real link to come).*

This repository contains the necessary code for reproducing results from the paper *First-year distribution and movement rates of PIT-tagged North East Atlantic mackerel (Scomber Scombrus) varies with timing, location, and fish size at release during the spawning season*. 

## Data 
All use of the data should cite Slotte et. al.(2021). 

The data used can be downloaded via API using functions from the [fishvice/taggart](https://github.com/fishvice/taggart) package. The package can be installed by 
```{r, eval = FALSE}
devtools::install_github("fishvice/taggart", dependencies = FALSE)
```
Due to some no longer maintained dependent packages, we have also copied the necessary functions to download the data in the *R/download_data_functions.R* file. 

The current data in *Data/current.nc* is average monthly surface current information (Northward and Eastward sea water velocity), from [Copernicus Marine Service](http://marine.copernicus.eu). 


## References

1. Ono, Kotaro, Sondre Hølleland, Aril Slotte, ..., 2021, *First-year distribution and movement rates of PIT-tagged North East Atlantic mackerel (Scomber Scombrus) varies with timing, location, and fish size at release during the spawning season*, Working paper. 
2. Slotte, Aril ... , 2021,.....




## Authors' github accounts

**Kotaro Ono** - [kotkot](https://github.com/kotkot)

**Sondre Hølleland** - [holleland](https://github.com/holleland)

## License

This project is licensed under the GNU GPLv3 License - see [LICENSE.md](LICENSE.md) for details. 
The data is licenced under .... **Link to data site here**.



